Depletion capabilities in the OpenMC Monte Carlo particle transport code

### 2020-05-01 manuscript.tex
Cite previous works coupling OpenMC with depletion
Change IPF CRAM outline to use algorithm environment

Mention isotalo papers

Mention previous depletion coupling with OpenMC (IMPC-Depletion, OpenBU, AMAC,
etc.)

@@

As we saw in \cref{sec:time_integration}, numerically integrating
\cref{eq:depletion-matrix} requires evaluating one or more matrix exponentials.
OpenMC uses the Chebyshev rational approximation method (CRAM), which was
introduced in a series of papers by Pusa~\citep{pusa2010nse,pusa2011nse}, to
evaluate matrix exponentials. In particular, OpenMC utilizes an incomplete
partial fraction (IPF) form~\citep{pusa2016nse} of CRAM that provides a good
balance of numerical stability and efficiency. In this representation the matrix
exponential is approximated as
\begin{equation}
    e^{\mathbf{A}t} \approx \alpha_0 \prod\limits_{\ell=1}^{k/2} \left (
    \mathbf{I} + 2 \text{Re} \left ( \widetilde{\alpha}_\ell \left (\mathbf{A}t
    - \theta_\ell \mathbf{I} \right )^{-1} \right ) \right )
\end{equation}
where $k$ is the order of the approximation and $\alpha_0$,
$\widetilde{\alpha}_\ell$, and $\theta_\ell$ are coefficients that have been
tabulated for orders up to $k=48$. Rather than computing the full approximation
and then multiplying it by a vector, the following algorithm\footnote{The
original description of the algorithm presented by \citet{pusa2016nse} contains
a typo.} is used to incrementally apply the terms within the product:
\begin{enumerate}
\item $\mathbf{n} \gets \mathbf{n_0}$
\item For $\ell = 1, 2, \dots, k/2$
  \begin{itemize}
   \item $\mathbf{n} \gets \mathbf{n} + 2\text{Re}(\widetilde{\alpha}_\ell
     (\mathbf{A}t - \theta_\ell)^{-1})\mathbf{n}$
  \end{itemize}
\item $\mathbf{n} \gets \alpha_0 \mathbf{n}$
\end{enumerate}
The $k$\ th order approximation for CRAM requires solving $k/2$ sparse linear
systems. OpenMC relies on functionality from scipy.sparse.linalg for solving the
linear systems.

>>>>

Mention Isotalo papers

Lots of community efforts toward coupled transport-depletion calculations with
OpenMC~\citep{gul2017ane,lanversin2017icone,lanversin2019phd,liu2019nst,zhuang2020pne,zhao2020ned,zhang2020ane}.

@@

As we saw in \cref{sec:time_integration}, numerically integrating
\cref{eq:depletion-matrix} requires evaluating one or more matrix exponentials.
OpenMC uses the Chebyshev rational approximation method (CRAM), which was
introduced in a series of papers by Pusa~\citep{pusa2010nse,pusa2011nse}, to
evaluate matrix exponentials. In particular, OpenMC utilizes an incomplete
partial fraction (IPF) form~\citep{pusa2016nse} of CRAM that provides a good
balance of numerical stability and efficiency. In this representation the matrix
exponential is approximated as
\begin{equation}
    e^{\mathbf{A}t} \approx \alpha_0 \prod\limits_{\ell=1}^{k/2} \left (
    \mathbf{I} + 2 \text{Re} \left ( \widetilde{\alpha}_\ell \left (\mathbf{A}t
    - \theta_\ell \mathbf{I} \right )^{-1} \right ) \right )
\end{equation}
where $k$ is the order of the approximation and $\alpha_0$,
$\widetilde{\alpha}_\ell$, and $\theta_\ell$ are coefficients that have been
tabulated for orders up to $k=48$. Rather than computing the full approximation
and then multiplying it by a vector, the following algorithm\footnote{The
original description of the algorithm presented by \citet{pusa2016nse} contains
a typo.} is used to incrementally apply the terms within the product:
\begin{algorithm}[H]
  \caption{Incomplete partial fraction form of CRAM.}
  \label{alg:cram}
  \begin{algorithmic}[1]
    \State $\mathbf{n} \gets \mathbf{n_0}$
    \For{$\ell \gets 1$ \textbf{to} $k/2$}
      \State $\mathbf{n} \gets \mathbf{n} + 2\text{Re}(\widetilde{\alpha}_\ell
        (\mathbf{A}t - \theta_\ell)^{-1})\mathbf{n}$
    \EndFor
    \State $\mathbf{n} \gets \alpha_0 \mathbf{n}$
  \end{algorithmic}
\end{algorithm}
The $k$\ th order approximation for CRAM requires solving $k/2$ sparse linear
systems. OpenMC relies on functionality from scipy.sparse.linalg for solving the
linear systems.
